\pkg{cv}: An \proglang{R} Package for Cross-Validation of Regression Models

### 2024-01-04 scratch/notes_john/JSS-article/JSS-article-reduced.Rmd
tweak loading of lme4

The initial mixed-effects model that we fit to the data is a simple random-intercepts model:
```{r include=FALSE, echo=FALSE}
library(lme4) # necessary for some reason to knit vignette in RStudio, harmless otherwise
```
```{r}
# random intercept only:
mod.0 <- lmer(y ~ 1 + (1 | group), Data)
summary(mod.0)
```

>>>>

The initial mixed-effects model that we fit to the data is a simple random-intercepts model:

```{r}
# random intercept only:
mod.0 <- lmer(y ~ 1 + (1 | group), Data)
summary(mod.0)
```

### 2024-01-04 scratch/notes_john/JSS-article/JSS-article-reduced.tex
tweak loading of lme4

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 838816
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.36368
bias-adjusted cross-validation criterion = 19.34363
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}

>>>>

Residual standard error: 4.374 on 389 degrees of freedom
Multiple R-squared:  0.6876,    Adjusted R-squared:  0.686 
F-statistic:   428 on 2 and 389 DF,  p-value: < 2.2e-16
\end{CodeOutput}
\begin{CodeInput}
R> cv(m.auto)
\end{CodeInput}
\begin{CodeOutput}
R RNG seed set to 866709
\end{CodeOutput}
\begin{CodeOutput}
10-Fold Cross Validation
method: Woodbury
criterion: mse
cross-validation criterion = 19.27395
bias-adjusted cross-validation criterion = 19.25863
full-sample criterion = 18.98477 
\end{CodeOutput}
\end{CodeChunk}
